Crowdy: Social Crowd Visualization

### 2011-04-28 docs/crowdy_gui.tex
fixed pics in report

\begin{figure}
\centering
\epsfig{file=img/TimelineView.eps, width= 250pt }
\caption{Timeline View}
\label{fig:Timeline View}
\end{figure}

\begin{figure}
\centering
\epsfig{file=img/CrowdViewInTimeline.eps, width= 250pt }
\caption{Crowd View In Timeline}
\label{fig:CrowdViewInTimeline}
\end{figure}

We apply the Simile Timeline library which is developed by MIT's Computer
Science and Artificial Intelligence Laboratory. The timeline as shown in figure \ref{fig:TimelineView} shows all of the
crowds at a given time span.  The timeline allows the analyist to zoom in on a
specific time, and move forward and backward thorough time.  The visualization
shows how long the crowd lasts, and the size of the crowd. We may make the
crowd taller or shorter based on the size of the crowd.  We will also display a
few keywords from each crowd. After a crowd in the timeline is clicked, a pop up ``Crowd View'' window will show the detailed information of this particular crowd (Figure \ref{}).

@@

\begin{figure}
\centering
\epsfig{file=img/ListView.eps, width= 250pt }
\caption{Overall List View}
\label{fig:ListView}
\end{figure}

@@

\begin{figure}
\centering
\epsfig{file=img/Search.eps, width= 250pt }
\caption{Search}
\label{fig:Search}
\end{figure}
In the search function of the system, we provide a main search box in which 
users can type a textual query to search for crowds which contains the query.
Besides, users can also click the link of advanced search, so that they can 
choose options of words, time period of crowd, size of crowd, presentation ways,
and results they would like to see per page. The layout is shown in figure \ref{fig:Search}. We maintain indices for each kind
of queries in the MongoDB database, so that we can efficiently return the results
to users. Whenever a query is issued, the systems send a HTTP GET request to the
backend, and the server would return the corresponding search results.

In our future direction, we will also provide query options like location, user's
screen name. So that users can search crowds that are in a specific city or an 
area, and also search crowds that a specific user is involved in.

@@

\begin{figure}
\centering
\epsfig{file=img/NetworkInList.eps, width= 250pt }
\caption{Network View in List}
\label{fig:NetworkInList}
\end{figure}

\begin{figure}
\centering
\epsfig{file=img/TweetsInList.eps, width= 250pt }
\caption{Tweets View in List}
\label{fig:TweetInList}
\end{figure}

\begin{figure}
\centering
\epsfig{file=img/GraphInList.eps, width= 250pt }
\caption{Graph View in List}
\label{fig:GraphInList}
\end{figure}
When an analyst clicks a crowd in the list, timeline, or map view, we show an
expanded view of the crowd. This is a form of progressive disclosure, where we
give the analyst more information as they need it.

>>>>

\begin{figure}
\centering
\includegraphics[width=\linewidth]{imgs/TimeLineView.png}
\caption{Timeline View}
\label{fig:TimelineView}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{imgs/CrowdViewInTimeLine.png}
\caption{Crowd View In Timeline}
\label{fig:CrowdViewInTimeline}
\end{figure}

We apply the Simile Timeline library which is developed by MIT's Computer
Science and Artificial Intelligence Laboratory. The timeline as shown in figure \ref{fig:TimelineView} shows all of the
crowds at a given time span.  The timeline allows the analyist to zoom in on a
specific time, and move forward and backward thorough time.  The visualization
shows how long the crowd lasts, and the size of the crowd. We may make the
crowd taller or shorter based on the size of the crowd.  We will also display a
few keywords from each crowd. After a crowd in the timeline is clicked, a pop up ``Crowd View'' window will show the detailed information of this particular crowd (Figure \ref{fig:CrowdViewInTimeline}).

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{imgs/ListView.png}
\caption{Overall List View}
\label{fig:ListView}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{imgs/Search.png}
\caption{Search}
\label{fig:Search}
\end{figure}
In the search function of the system, we provide a main search box in which 
users can type a textual query to search for crowds which contains the query.
Besides, users can also click the link of advanced search, so that they can 
choose options of words, time period of crowd, size of crowd, value of clustering coefficient of crowds,
and results they would like to see per page. The layout is shown in figure \ref{fig:Search}. We maintain indices for each kind
of queries in the MongoDB database, so that we can efficiently return the results
to users. Whenever a query is issued, the systems send a HTTP GET request to the
backend, and the server would return the corresponding search results.

In our future direction, we will also provide query options like location, user's
screen name, . So that users can search crowds that are in a specific city or an 
area, and also search crowds that a specific user is involved in.

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{imgs/NetworkInList.png}
\caption{Network View in List}
\label{fig:NetworkInList}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{imgs/TweetsInList.png}
\caption{Tweets View in List}
\label{fig:TweetInList}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{imgs/GraphInList.png}
\caption{Graph View in List}
\label{fig:GraphInList}
\end{figure}
When an analyst clicks a crowd in the list, timeline, or map view, we show an
expanded view of the crowd. This is a form of progressive disclosure, where we
give the analyst more information as they need it.
